Usage metrics

### 2021-03-01 analysis/usage.Rmd
Coverage per package

We compute the frequency of evals by package. This shows that some packages
hardly use eval while other use it intensly. The numbers are "for all runs",
this means that a popular package may be triggered by more runs and thus
have higher frequencies. We will later control for this by looking at individual 
call sites.

@@

>>>>

We compute the frequency of evals by package. This shows that some packages
hardly use eval while other use it intensely. The numbers are "for all runs",
this means that a popular package may be triggered by more runs and thus
have higher frequencies. We will later control for this by looking at individual 
call sites.

@@

```{r coverage-per-package}
cov_packages <- static_call_sites_per_package %>%
  left_join(sites_per_package, by = c("package" = "ev_package"), suffix = c("_static", "_tracer")) %>% 
  mutate(n_tracer = replace_na(n_tracer, 0L))

# if n_static < n_tracer, adjust n_tracer to n_static
# Probably due to higher-order functions taking some eval
cov_packages <- cov_packages %>%
  mutate(n_static = if_else(n_static < n_tracer, n_tracer, n_static))

cov_packages <- cov_packages %>% mutate(coverage = 100 * n_tracer / n_static)

cov_packages %>% ggplot() +
  geom_histogram(aes(x = coverage)) + 
  labs(x = "coverage (%)")

ggsave(path(PLOT_DIR, "coverage_per_package.pdf"))
```
